Article figures

### 2020-12-03 src/article_figures.Rmd
Updated the table in md

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("economic_effect_functions.R")
save_figs = TRUE
fig_path="~/FRCBS/results-for-eba-paper/pdf"
```

@@

  print(combined_variables)

@@

get_threshold_df <- function() {

  t6 <- tibble(
      Id = factor(all_ids),
      type = factor("Threshold"),
      value = c(0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.2, 0.1, 0.4, 0.6,   0.2, 0.3))
  t12 <- tibble(
      Id = factor(all_ids),
      type = factor("Threshold"),
      value = c(0.2, 0.2, 0.1, 0.1, 0.1, 0.2, 0.3, 0.3, 0.8, 0.8,   0.4, 0.5)
  )
  t <- bind_rows(t6, t12)
  t <- t %>%
    mutate(low=value, 
           high=value,
           sex=factor(str_split_fixed(Id, "-", 3)[,2], levels=c("female", "both", "male")),
           #model=factor(str_split_fixed(Id, "-", 3)[,3])
           model=rep(c("t6", "t12"), each=length(all_ids))
           )
  return(t)
}

@@

  dummy <- dummy %>%
    mutate(variable = fct_recode(variable, !!!new_names))
  print(dummy)
  print(df)

@@

```{r}
df <- read_csv("~/FRCBS/results-for-eba-paper/raw-data-2020-11-30.csv")
df <- df %>% 
  pivot_wider(names_from=c("variable", "type"), values_from=value, names_glue="{variable} {type}")
names(df) <- str_remove(names(df), " value$")
df %>%
  select("Id", "F1", "F1 low", "F1 high", "threshold6", "threshold12", "E6", "E6 low", "E6 high", "E12", "E12 low", "E12 high")
```

```{r, eval=FALSE, include=FALSE}
# jarkko_test <- function(male_posterior, female_posterior, variables,
#                                            filename=NULL,
#                                            width = 180,  # width of the combined figure in millimetres
#                                           base_size = 11
# ) {
#   rrfFit_roc <- load_single("~/FRCBS/interval_prediction/results/rrfFit_roc.rdata")
# 
#   combined_variables <- tibble(Pretty=c(variables, "Life time donations", "Sex", "First Hb")) %>%
#     mutate(stripe=factor(row_number()%%2),    # this is used to make the gray/white background
#            Pretty=factor(Pretty, levels=Pretty))
# 
#   result <- get_dlmm_df(male_posterior, female_posterior, variables, combined_variables)
#   varimp <- get_rf_df(rrfFit_roc, descript, combined_variables)
# 
#   result <- result %>%
#     mutate(Pretty=fct_rev(Pretty))
# 
#   var_imp <- varimp %>%
#     mutate(Pretty=fct_rev(Pretty),
#            mean=Importance,
#            low=ifelse(is.na(Importance), NA, 0),
#            high=Importance)
# 
#   final <- bind_rows(`Regression coefficient`=result, Importance=var_imp, .id="method") %>%
#     mutate(method=factor(method, levels=c("Regression coefficient", "Importance"))) %>%
#     select(-Importance, -Variable, stripe)
# 
# #   final <- tibble(
# #             method = c("Regression coefficient",
# #                        "Regression coefficient","Importance"),
# #             Pretty = factor(c("Days to previous full blood donation","Days to previous full blood donation",
# #                        "Days to previous full blood donation")),
# #             #gender = c("male", "female", "both"),
# #               mean = c(0.0152091681221149,
# #                        0.0445741103338152,0.0255604042298423),
# #                low = c(0.00691102953212081, 0.0353192308283623, 0),
# #               high = c(0.0240855557569598,
# #                        0.0537929726515129,0.0255604042298423)
# # )
#   
#   #combined_variables <- tibble(Pretty=factor("Days to previous full blood donation"), stripe=factor(1))
#   
#   print(final)         
#   print(combined_variables)
#   vars <- c("Days to previous full blood donation", "Age", "Previous donation deferred", "Year")
#   plot <- final %>% #filter(Pretty %in% vars) %>%
#     ggplot(aes(color=gender)) +
#     geom_rect(data=combined_variables %>% filter(stripe==1),
#               mapping=aes(#ymax = as.numeric(Pretty) + 0.5,
#                           #ymin = as.numeric(Pretty) - 0.5
#                           ymax = as.numeric(Pretty) + 0.5,
#                           ymin = as.numeric(Pretty) - 0.5),
#               fill = "blue", 
#               #position="identity",
#               xmin=-Inf, xmax=Inf, alpha = 0.1, inherit.aes = FALSE) +
#     ggstance::geom_pointrangeh(#data=final, 
#                                mapping=aes(y=Pretty, x=mean, xmin=low, xmax=high),
#                                #position=position_dodge2(0.8)
#                                position=position_dodge2(width=0.8, padding=0.1)
#                                ) +
#     scale_y_discrete() +
#     facet_wrap("method", scales = "free_x") +
#     #coord_flip() +
#     theme_classic(base_size = base_size) 
# 
#   return(list(plot=plot, final=final))
# }
# 
# res <- jarkko_test(male_posterior, female_posterior, variables, filename=filename)
# final <- res$final
# g <- res$plot
# g
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("economic_effect_functions.R")
library(knitr)
library(tidyverse)
save_figs = TRUE
fig_path="~/FRCBS/results-for-eba-paper/pdf"
```

@@

  #print(combined_variables)

@@

# get_threshold_df <- function() {
#   
#   t6 <- tibble(
#       Id = factor(all_ids),
#       type = factor("Threshold"),
#       value = c(0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.2, 0.1, 0.4, 0.6,   0.2, 0.3))
#   t12 <- tibble(
#       Id = factor(all_ids),
#       type = factor("Threshold"),
#       value = c(0.2, 0.2, 0.1, 0.1, 0.1, 0.2, 0.3, 0.3, 0.8, 0.8,   0.4, 0.5)
#   )
#   t <- bind_rows(t6, t12)
#   t <- t %>%
#     mutate(low=value, 
#            high=value,
#            sex=factor(str_split_fixed(Id, "-", 3)[,2], levels=c("female", "both", "male")),
#            #model=factor(str_split_fixed(Id, "-", 3)[,3])
#            model=rep(c("t6", "t12"), each=length(all_ids))
#            )
#   return(t)
# }

@@

  dummy <- dummy %>%
    mutate(variable = fct_recode(variable, !!!new_names))
  #print(dummy)
  #print(df)

@@

```{r}
df <- read_csv("~/FRCBS/results-for-eba-paper/raw-data-2020-12-01.csv")
df <- df %>% 
  pivot_wider(names_from=c("variable", "type"), values_from=value, names_glue="{variable} {type}")
names(df) <- str_remove(names(df), " value$")
df2 <- df %>%
  select("Id", "F1", "F1 low", "F1 high", "threshold6", "threshold12", "E6", "E6 low", "E6 high", "E12", "E12 low", "E12 high")
kable(df2, digits=2)
```
